The error in Bayesian phylogenetic reconstruction when speciation is not instantaneous

### 2018-09-17 article.tex
Add Maturana text temporarily

>>>>

From Maturana et al:
Although the marginal likelihood is generally ignored in parameter inference, it plays a key role in model
selection: it is a measure of the goodness of fit. Indeed, it is the probability of the data given the model,
i.e., it is by definition a measure of model fit. The marginal likelihood acts as the normalisation constant in
the posterior distribution making it a probability density function. Thus, this quantity is a multidimensional
integral of the prior distribution times the likelihood function over the parameter space. MCMC methods
used for parameter estimation within a model use only ratios of posterior densities, and are therefore unable
to measure its normalisation in general.
Unlike maximum likelihood, which represents the model fit at a single point, this quantity stands for an average
of how well the model fits the data. By being an average of the likelihood function with respect to the prior,
the model with the greatest evidence might be different from the model with the highest likelihood because
the prior could down-weight some regions of parameter space. Also, the marginal likelihood is sensitive to the
size of the region over which the likelihood is high. As a result, both methods could favour different models.
Despite its important role in model selection, the marginal likelihood is usually analytically intractable and
has to be approximated by numerical methods.
